---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%",
  fig.align = "center"
)
```

# covid19peakfit package

<!-- badges: start -->
<!-- badges: end -->

The `covid19peakfit` package fits an experimental model to estimate the peak of confirmed infected with COVID-19. 

This package is part of [UNICAMP's BCB Lab](https://github.com/labbcb/covid19unicamp) task force against COVID-19.


## Installation

Install from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("gabrielfranco89/covid19peakfit")
```
## Example

To visualize data and have an idea for initial parameters:

```{r example}
library(covid19peakfit)
df <- subset(korea_covid19, subset = date <= "2020-02-27")

## Must prep data before graph
df_prep <- prep_data(df, cum_cases = "cum_cases", date_var = "date")
visu(df_prep)
```

To fit model:

```{r fit}
fit <- covid19peakfit(data = df,
                      cum_cases = "cum_cases",
                      date_var = "date",
                      init_pars = c(10000, 40, 1),
                      lim_inf = c(max(df$cum_cases),
                                  40,
                                  0),
                      weights = c(.1,.1,3))

fit$plot
```

- Estimated peak day: `r df$date[1] + fit$pars[2]`
- Real peak day: 2020-03-04


You can also check for future days:

```{r future, warning=FALSE}
future(fit, n_fut=10)
```

# Links

- BCB Lab: https://github.com/labbcb/covid19unicamp
- `datacovidbr` package for COVID-19 data download for R: https://github.com/Freguglia/datacovidbr
- Estimativa do pico de casos de COVID-19 em Campinas (in Portuguese): http://bcblab.org/covid19unicamp/analise_curvas/campinas
